---
title: Data Rectangling with jq
author: Carl Boettiger
date: '2017-12-11'
categories: [R]
tags: [R, json]
---


> "Data rectangling": the process of turning highly nested data structures (e.g. JSON, XML) into a tabular format.


Data rectangling is a brilliant turn of phrase coined by Jenny Bryan (UBC, RStudio) and leader in the #rstats community.  [Recording](https://speakerdeck.com/jennybc/data-rectangling) or [slides](https://speakerdeck.com/jennybc/data-rectangling) of Jenny's talk on the subject give a much better intro to the idea and working with this in R, particularly through the `purrr` package.  

As nice as `purrr` is for the task, I've recently found that the [`jqr` package](https://github.com/ropensci/jqr) from [Scott Chamberlain](https://scottchamberlain.info/) and co can be a much easier way to go about rectangling your JSON.  Here's a quick comparison based on an example from the [lesson](https://dcl-2017-04.github.io/curriculum/rectangling.html) Hadley Jenny have on Data Rectangling.

```{r include=FALSE}
library(knitr)
library(DT)
knit_print.data.frame <- function(x, ...) {
  knitr::knit_print(DT::datatable(x), ...)
}
```


```{r message=FALSE}
#devtools::install_github("jennybc/repurrrsive")
library(jsonlite)
library(tidyverse)
library(repurrrsive)
library(jqr)
```




## Using purrr


```{r }
gh_flat <- gh_repos %>% flatten()  # abandon nested structure and hope we didn't need it

gh_tibble <- tibble(
  name =     gh_flat %>% map_chr("name"),
  issues =   gh_flat %>% map_int("open_issues_count"),
  wiki =     gh_flat %>% map_lgl("has_wiki"),
  homepage = gh_flat %>% map_chr("homepage", .default = ""),
  owner =    gh_flat %>% map_chr(c("owner", "login"))
)

gh_tibble %>% datatable()
```

Note we need to be explicit about missing value defaults and types.


## Using jqr

Note that we can simply exploit the object typing already encoded in the data (`int`, `lgl`,`chr`)

```{r message=FALSE}
f <- system.file("extdata/gh_repos.json", package="repurrrsive")

read_file(f) %>% 
 jq('.[][] | { 
    name: .name, 
    issues: .open_issues_count,
    wiki: .has_wiki,
    homepage: .homepage,
    owner: .owner.login
    } ') %>% 
  jqr::combine() %>% # single json file
  fromJSON()  %>% DT::datatable()
```

This example only touches the surface of the `jq` syntax.  The [jq manual](https://stedolan.github.io/jq/manual/) provides a nice overview of this intuitive syntax.  `jq` can also perform a wide range of data processing on the elements: including conditionals, comparisons, regular expressions, math, and so forth.  While these are great, most R users will want to learn just enough `jq` syntax to get back a nice data rectangle, and then `dplyr` can take over.  
