---
layout: post
published: false

---

```{r}
library("nimble")
library("sde")
```

```{r}
set.seed(123)
d <- expression(0.5 * (10-x))
s <- expression(1) 
data <- as.data.frame(sde.sim(X0=6,drift=d, sigma=s, T=100, N=400))
```


```{r}
code <- modelCode({
     K ~ dunif(0.01, 40.0)
    r0 ~ dunif(0.01, 20.0)
  stdQ ~ dunif(1e-6, 100)

  iQ <- 1 / (stdQ * stdQ);

  x[1] ~ dunif(0, 10)
  for(t in 1:(N-1)){
    mu[t] <- log(x[t]) + r0 * (1 - x[t]/K) 
    x[t+1] ~ dlnorm(mu[t], iQ) 
  }
})

constants <- list(N = length(data$x))
inits <- list(K = 6, r0 = 1, stdQ = 1)

Rmodel <- nimbleModel(code=code, constants=constants, data=data, inits=inits)
```

create MCMC specification and algorithm

```{r}
mcmcspec <- MCMCspec(Rmodel)
Rmcmc <- buildMCMC(mcmcspec)

## compile model and MCMC algorithm
Cmodel <- compileNimble(Rmodel)
Cmcmc <- compileNimble(Rmcmc, project = Cmodel)

## execute MCMC algorithm and extract samples
Cmcmc(10000)
samples <- as.matrix(nfVar(Cmcmc, 'mvSamples'))
```

Query some details regarding our specification (set by default)

```{r}
mcmcspec$getSamplers()
mcmcspec$getMonitors()
```


Some quick impressions: 

- Strange that `Rmodel` call has to be repeated before we can set up a custom MCMC ([nimble docs](http://r-nimble.org/examples)).  How/when was this object altered since it was defined in the above code?  Seems like this could be problematic for interpreting / reproducing results?

- What's going on with `getSamplers()` and `getMonitors()`? Guessing these are in there just to show us what the defaults will be for our model?

- why do we assign `Cmodel` if it seems we don't use it? (the compilation needs to be done but isn't explicitly passed to the next step).  Seems we can use `Cmodel` instead of `Rmodel` in the `Cmcmc <- compileNimble(Rmcmc, project = Cmodel)`, which makes the dependency more explicit, at least that notation is more explicit.  Seems like it should be possiple to omit the first `compileNimble()` and have the second call the `compileNimble` automatically if it gets an object whose class is that of `Rmodel` instead?

- Repeated calls to `Cmcmc` seem not to give the same results.  Are we adding additional mcmc steps by doing this?

- Thinking an `as.data.frame` would be nicer than `as.matrix` in the `nfVar` `mvSamples` coercion.  

- Don't understand what `simulate` does (or why it always returns NULL?). 

