%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Freeman Curriculum Vitae
% XeLaTeX Template
% Version 2.0 (19/3/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%!TEX program = xelatex
% NOTICE: This template must be compiled with XeLaTeX, the line above should
% ensure this happens automatically but if it doesn't you will need to specify 
% XeLaTeX as the engine in your editor or script
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Font size, can be: 10pt, 11pt or 12pt

\input{structure.tex} % Include the file that specifies the document structure

% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example right footer:
%\rfoot{\color{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------

\begin{document}

\begin{paracol}{2} % Begin the multi-column environment

%----------------------------------------------------------------------------------------
%	NAME AND CURRICULUM VITAE TEXT
%----------------------------------------------------------------------------------------

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\centering % Centre text
	{\sffamily\Huge Dr. Carl Boettiger}\\\medskip % Your name
	{\Huge\color{headings}\cvtextfont Curriculum Vitae}
}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}

% Blank \workposition command to add another job:

%\workposition{} % Duration
%{} % FT/PT (full time or part time)
%{} % Employer
%{} % Job title
%{} % Description

% All 5 parameters must be supplied but any can be empty if you don't need them

%------------------------------------------------

\workposition{Current, from July 2015} % Duration
{FT} % FT/PT (full time or part time)
{University of California, Berkeley} % Employer
{Assistant Professor} % Job title
{Department of Environmental Science, Policy and Management} % Description

%------------------------------------------------

\workposition{2013-2015} % Duration
{FT} % FT/PT (full time or part time)
{University of California, Santa Cruz} % Employer
{NSF Post-doctoral Scholar} % Job title
{Department of Applied Mathematics and Statistics}  % Description

%------------------------------------------------

\vspace{-\baselineskip}\medskip % Standardise the whitespace after this section and before the next (the custom command adds too much otherwise)


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education} 

% Blank \educationentry{} command to add another degree:

%\educationentry{} % Duration
%{} % Degree
%{} % Honours, achievements or distinctions (e.g. first class honours)
%{} % Department
%{} % Institution

% All 5 parameters must be supplied but any can be empty if you don't need them

%------------------------------------------------

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

	%------------------------------------------------
	
	\educationentry{2007 -- 2012} % Duration
	{Doctor of Philosophy} % Degree
	{} % Honours, achievements or distinctions (e.g. first class honours)
	{Population Biology. Mentor: Alan Hastings} % Department
	{University of California, Davis} % Institution
	
	%------------------------------------------------
	
	\educationentry{2003 -- 2007} % Duration
	{Bachelors of Physics} % Degree
	{with Honours} % Honours, achievements or distinctions (e.g. first class honours)
	{Physics, w/ Certs. in Applied Mathematics} % Department
	{Princeton University} % Institution
	
	%------------------------------------------------

\end{supertabular}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\section{Grants}

% Example \tableentry{} command to add another line:
%\tableentry{Heading}{Content}{spaceafter}
% All 3 parameters must be supplied but any can be empty if you don't need them
% A "spaceafter" value in the third parameter will add some vertical space -- this is to be used between headings

%------------------------------------------------

\begin{supertabular}{rl} % Start a table with two columns, the table will ensure everything is aligned

  \educationentry{2018 -- 2022}{National Science Foundation,  \$1,301,737}{}{T. Bowles, A. Iles, C. Kremen, C. Boettiger}{Coupled Natural Human Systems \href{https://nsf.gov/awardsearch/showAward?AWD_ID=1824871}{\#CNH-1824871}}
	
  \educationentry{2019 -- 2021}{Helmsley Charitable Trust,  \$1,000,000}{}{K. Ram, C. Boettiger, S. Chamberlain}{\href{https://ropensci.org}{The rOpenSci Project}}

  \educationentry{2018}
  {Berkeley Institute for Data Science, \$67,000}
  {}
  {C. Boettiger, R. Gillespie, R. Nielsen}{\hspace{.1pt}}


  \educationentry{2018 -- 2021}
  {The Hellman Foundation, \$37,600}
  {}
  {C. Boettiger}
  {Junior Faculty Fellowship}
  
  
  \educationentry{2018 -- 2019}
  {Berkeley Collegium \$16,867}
  {}
  {C. Boettiger}
  {Narrowing the Gap Between Teaching and Research}

  \educationentry{2016 - 2019}{James S McDonnell Foundation, \$200,000}{}{(Awarded to Allison Barner, who brought it to my team)}{\href{https://www.jsmf.org/grants/20150024/}{Post-doctoral Fellowship in Complex Systems}}

  \educationentry{2015 -- 2018}{Helmsley Charitable Trust,  \$2,875,071}{}{K. Ram, C. Boettiger, S. Chamberlain} {\href{https://ropensci.org}{The rOpenSci Project}, \#2016PG-BRI004}

  \educationentry{2015 -- 2018}{National Science Foundation, \$165,782}{}{C. Boettiger, M. Jones}{The CodeMeta Project \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1549758}{\#ACI-1549758}}

  \educationentry{2014}{Alfred P. Sloan Foundation, \$300,000}{}{K. Ram, C. Boettiger, S. Chamberlain}{The rOpenSci Project Phase II funding}  

  \educationentry{2013}{Alfred P. Sloan Foundation, \$180,000}{}{K. Ram, C. Boettiger, S. Chamberlain}{The rOpenSci Project Phase I funding}  

  \educationentry{2013 -- 2015}{National Science Foundation, \$138,000}{}{}
  {C Boettiger. \href{http://www.nsf.gov/pubs/2012/nsf12497/nsf12497.htm}{NSF Biology
  Post-doc}, \href{http://www.nsf.gov/awardsearch/showAward?AWD_ID=1306697}{\#DBI-1306697}}

  \educationentry{2009}
  {National Academy of Sciences \$8,000}
  {}
  {IIASA YSSP fellowship}
  {OISE-0738129}.

  \educationentry{2008 -- 2012}
  {Department of Energy, \$149,000}
  {}
  {Computational Science Graduate Fellowship}
  {\href{https://www.krellinst.org/csgf/alumni/profile?n=boettiger2008}{\#DE-FG02-97ER25308}}

  %Managing ecosystems under extreme uncertainty. (2016 - 2019) NSF
  %\textbf{XSEDE} TG-DEB160003. NSF Estimated value of computing
  %resources: \$34,558

 % Reproducible and Collaborative Data Science. NSF \textbf{XSEDE}
 % TG-DEB160021. (2016 - 2019) NSF Estimated value of computing
 % resources: \$20,028

\end{supertabular}

\section{Invited Talks and Workshops}

\begin{supertabular}{rl}

\tableentry{2019}{Ecological Society of America \href{https://eco.confex.com/eco/2019/meetingapp.cgi/Session/15321}{invited OOS}, Louisville, KY}{}
    \tableentry{}{\href{https://ecoforecast.org/efi2019/}{Ecological Forecasting
  Initiative}, Washington DC.}{}
    \tableentry{}{\href{http://www.nimbios.org/workshops/WS_transients}{NIMBioS
       Workshop}, UT Knoxville, TN.}{}
    \tableentry{}{\href{https://serc.carleton.edu/eddie/earthecosystems/eddieevents/workshops/barriers_solutions/index.html}{Project
      EDDIE} keynote speaker, Carlton, Northfield MN.}{}
    \tableentry{}{\href{https://github.com/si2-urssi/software-credit}{URSSI Workshop}, NCEAS, Santa Barbara, CA.}{}
    \tableentry{}{\href{https://www.compassscicomm.org}{COMPASS Workshop} Asilomar, CA}{spaceafter}

\tableentry{2018}{\href{https://si2-pi-community.github.io/2018-meeting/}{NSF SI2 PIs
  Meeting}, Washington, DC.}{}
\tableentry{}{\href{http://unconf18.ropensci.org}{rOpenSci unconference}, Seattle,
  WA.}{}
\tableentry{}{\href{https://teaching.berkeley.edu/programs/transforming-stem-teaching-faculty-learning-program/become-flp-faculty-fellow}{FLP Fellows Workshop} Berkeley, CA.}{}
\tableentry{}{\href{https://graphxd.github.io/workshop/2018.html}{GraphXD},
  Berkeley, CA}{}
\tableentry{}{\href{https://www.idigbio.org/wiki/index.php/Digital_Data_in_Biodiversity_Research_Conference,_Berkeley}{Digital
  Data in Biodiversity} (co-org), Berkeley CA.}{}
\tableentry{}{\href{https://eco.confex.com/eco/2018/meetingapp.cgi/Session/14034}{ESA Invited Symposium} (Organizer). New Orleans, LA.}{}
\tableentry{}{ Nonlinear Forecasting, NOAA SFSC, Santa Cruz, CA}{spaceafter}

\tableentry{2017}{\href{https://cross.ucsc.edu/cross-events/research-symposium/2017-symposium/}{CROSS
  Symposium Speaker} Santa Cruz, CA}{}
\tableentry{}{\href{http://www.ncsa.illinois.edu/Conferences/ImagineU/participants.html}{Imagining
  Tomorrow's University} Chicago, IL}{}
\tableentry{}{\href{http://unconf17.ropensci.org}{rOpenSci unconference}, Los
  Angeles, CA}{}
\tableentry{}{\href{https://dataoneorg.github.io/provathon-2017/}{DataONE}, Tamaya, NM.}{}
\tableentry{}{\href{https://bids.berkeley.edu/events/translational-data-science-workshop}{NSF
  Translational Data Science}, Berkeley, CA.}{spaceafter}


\tableentry{2016}{\href{http://sched.co/5wK5}{Force16 Codemeta Workshop} (organizer), Portland OR}{}
\tableentry{}{\href{https://codemeta.github.io}{CodeMeta NSF Workshop} (Organizer) Portland, OR.}{}
\tableentry{}{\href{http://unconf16.ropensci.org}{rOpenSci unconference}, San
  Francisco, CA}{spaceafter}


\tableentry{2015}{\href{http://ecows.oc.ntu.edu.tw/itnlws/}{Empirical Dynamical Modeling}, NTU, Taiwan}{}
\tableentry{}{Moore-Sloan Second Annual Data Science Summit}{}
\tableentry{}{\href{https://github.com/NCEAS/ds-workshop-2015}{Improving Data Intensive Training}, NCEAS, Santa Barbara, CA}{}
\tableentry{}{\href{http://www.nsf.gov/pubs/2015/nsf15562/nsf15562.htm}{NSF Big Data
  Hubs} Design Charette, Western Region}{}
\tableentry{}{\href{http://unconf.ropensci.org/}{rOpenSci unconference}, San
  Francisco CA}{}
\tableentry{}{\href{http://www.nimbios.org/workinggroups/WG_PDG}{NIMBIOS Working Group}, Knoxville TN}{spaceafter}

\tableentry{2014}{Global Change Biology, UC Berkeley, CA}{}
\tableentry{}{Zoology Seminar, University of Wisconsin, Madison, WI}{}
\tableentry{}{\href{http://dimacs.rutgers.edu/Workshops/GlobalChange/announcement.html}{DIMACS} Global Change, Berkeley CA}{}
\tableentry{}{ESPM Seminar, UC Berkeley, CA}{}
\tableentry{}{\href{http://ropensci.org/blog/2014/05/14/ropenhack/}{rOpenSci unconf}, San Francisco CA}{}
\tableentry{}{\href{https://github.com/Reproducible-Science-Curriculum/Reproducible-Science-Hackathon-Dec-08-2014}{Reproducible Science Curriculum}, NESCent, Durham, NC}{}
\tableentry{}{\href{http://wssspe.researchcomputing.org.uk/wssspe2/}{WSSSPE 2.0 Meeting}. New Orleans, LA}{}
\tableentry{}{Workflows Working Group, NCEAS, Santa Barbara, CA}{spaceafter}

\tableentry{2013}{
  \href{http://www.mbi.ohio-state.edu/2013/ws3description.html}{MBI}, invited speaker, Columbus, OH}{}
\tableentry{and}{Seminar speaker, WHOI, Woods Hole, MA}{}
\tableentry{prior}{Seminar speaker, Davis, CA}{}
 \tableentry{}{SSB Symposium, Evolution Conference, Ottawa, CAN}{}
 \tableentry{}{\href{http://isees.nceas.ucsb.edu}{ISEES}, Santa Barbara, CA}{spaceafter}


\end{supertabular}
  

\switchcolumn % Switch to the next paracol column

%----------------------------------------------------------------------------------------
%	COLOURED CONTACT DETAILS BOX
%----------------------------------------------------------------------------------------

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the colour box; fixed height to match the name/CV text to the left, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\colorbox{shade}{ % Create the coloured box
		\begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\raisebox{-1pt}{\faHome} & ESPM Department, University of California, 130 Mulford Hall \#3114 Berkeley, CA 94720 \\ % Address
			\raisebox{0pt}{\small\faEnvelope} & \href{mailto:cboettig@berkeley.eu}{cboettig@berkeley.edu} \\ % Email address
			\raisebox{-1pt}{\small\faDesktop} & \href{https://carlboettiger.info}{https://carlboettiger.info} \\ % Website
			\raisebox{-1pt}{\faGithub} & \href{https://github.com/cboettig}{https://github.com/cboettig} \\ % GitHub profile
			%\raisebox{-1pt}{\faLinkedinSquare} & \href{https://www.linkedin.com/in/username}{https://www.linkedin.com/in/username} \\ % LinkedIn profile
			% See fontawesome.pdf in the fonts folder for all icons you can use
		\end{supertabular}
	}
}


%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\section{Publications (32)}

% Example \longformdescription{} command to add another publication:

%\longformpublication{Reference (format this manually as desired)}

%------------------------------------------------
\longformpublication{
Milad Memarzadeh, Gregory L. Britten, Boris Worm, \textbf{Carl
  Boettiger} (2019). Rebuilding global fisheries under uncertainty.
  \emph{Proceedings of the National Academy of Sciences}.
  \href{https://doi.org/10.1073/pnas.1902657116}{doi:10.1073/pnas.1902657116}
}

\longformpublication{
  \textbf{Carl Boettiger}, Ryan Batt (2019). Bifurcation or state
  tipping: assessing transition type in a model trophic cascade.
  \emph{Journal of Mathematical Biology}.
  \href{https://doi.org/10.1007/s00285-019-01358-z}{doi:10.1007/s00285-019-01358-z}
  (\href{https://github.com/cboettig/bs-tipping/blob/master/paper/paper.pdf}{oa},
  \href{https://github.com/cboettig/bs-tipping}{code})
}

\longformpublication{
  Milad Memarzadeh, \textbf{Carl Boettiger} (2019). Resolving the
  Measurement Uncertainty Paradox in Ecological Management.
  \emph{American Naturalist}.
  \href{https://doi.org/10.1086/702704}{doi:10.1086/702704}.
  (\href{https://github.com/boettiger-lab/pomdp-intro/tree/master/manuscripts}{oa},
  \href{https://github.com/boettiger-lab/pomdp-intro}{code},
  \href{https://doi.org/10.5281/zenodo.2528507}{data})
}

\longformpublication{
  Dan Sholler, Karthik Ram, \textbf{Carl Boettiger}, Daniel S Katz
  (2019). Enforcing public data archiving policies in academic
  publishing: A study of ecology journals. \emph{Big Data \& Society}
  6(1) 1-18.
  \href{https://doi.org/10.1177/2053951719836258}{doi:10.1177/2053951719836258}
}

\longformpublication{
  \textbf{Carl Boettiger} (2019). Ecological Metadata as Linked Data.
  \emph{Journal of Open Source Software}, 4(34), 1276,
  \href{https://doi.org/10.21105/joss.01276}{doi:10.21105/joss.01276}
  (\href{https://doi.org/10.5281/zenodo.1442890}{software}).
}

\longformpublication{
  Katz, Allen, Barba, Berg, Bik, \textbf{Boettiger}, et al. (2018). The
  principles of tomorrow's university. \emph{F1000Research}, 7:1926
  \href{https://doi.org/10.12688/f1000research.17425.1}{doi:10.12688/f1000research.17425.1}.
  (32 co-authors.)
}

\longformpublication{
  Karthik Ram, \textbf{Carl Boettiger}, Scott Chamberlain, Noam Ross,
  Maelle Salmon, \& Stephanie Butland (2018). A Community of Practice
  Around Peer-review for Long-term Research Software Sustainability.
  \emph{Computing in Science \& Engineering}, 9615(c), 1--1.
  \href{https://doi.org/10.1109/MCSE.2018.2882753}{doi:10.1109/MCSE.2018.2882753}
}

\longformpublication{
  \textbf{Carl Boettiger} (2018). Managing Larger Data on a GitHub
  Repository. \emph{Journal of Open Source Software}, 3(29), 971,
  \href{https://doi.org/10.21105/joss.00971}{doi:10.21105/joss.00971}.
  (\href{https://doi.org/10.5281/zenodo.1432525}{software}).
}

%%% \switchcolumn % Switch to the next paracol column


\longformpublication{
  Milad Memarzadeh, \textbf{Carl Boettiger} (2018). Adaptive management
  of ecological systems under partial observability. \emph{Biological
  Conservation}. 224, 9-15.
  \href{https://doi.org/10.1016/j.biocon.2018.05.009}{doi:10.1016/j.biocon.2018.05.009}.
  (\href{https://github.com/boettiger-lab/pomdpplus}{software})
}

\longformpublication{
  \textbf{Carl Boettiger} (2018). From noise to knowledge: how
  randomness generates novel phenomena and reveals information.
  \emph{Ecology Letters}.
  \href{https://doi.org/10.1111/ele.13085}{doi:10.1111/ele.13085}
  (\href{https://github.com/cboettig/noise-phenomena/raw/master/paper/paper.pdf}{oa},
  \href{https://github.com/cboettig/noise-phenomena}{code},
  \href{https://doi.org/10.5281/zenodo.1219779}{data})
}

\longformpublication{
  \textbf{Carl Boettiger}, Dirk Eddelbuettel (2018). An Introduction to
  Rocker: Docker Containers for R. \emph{The R Journal}.
  \href{https://doi.org/10.32614/RJ-2017-065}{doi:10.32614/RJ-2017-065}
}

\longformpublication{
  \textbf{Carl Boettiger} (2017). Generating Codemeta Metadata for R
  Packages. \emph{The Journal of Open Source Software} 2 (19), 454,
  \href{https://doi.org/10.21105/joss.00454}{doi:10.21105/joss.00454}
}

\longformpublication{
  Getz, Marshall, Carlson, Giuggioli, Ryan, Romañach,
  \textbf{Boettiger}, Chamberlain, Larsen, D'Odorico, O'Sullivan (2017).
  Making ecological models adequate. \emph{Ecology Letters}. \\
  \href{https://doi.org/10.1111/ele.12893}{doi:10.1111/ele.12893}
}

\longformpublication{
  Ben Marwick, \textbf{Carl Boettiger}, Lincoln Mullen (2017). Packaging
  data analytical work reproducibly using R (and friends). \emph{The
  American Statistician}.
  \href{https://doi.org/10.1080/00031305.2017.1375986}{doi:10.1080/00031305.2017.1375986}.
  (\href{https://doi.org/10.7287/peerj.preprints.3192v1}{oa})
}

\longformpublication{
  Hampton, Jones, Wasser, Schuldhauer, Supp, Brun, Herandez,
  \textbf{Boettiger}, Collins, Gross, Fernandez, Budden, White, Teal,
  Labou, Aukema (2017). Skills and Knowledge for Data Intensive
  Research. \emph{BioScience}.
  \href{https://doi.org/10.1093/biosci/bix025}{doi:10.1093/biosci/bix025}.
  (\href{https://doi.org/10.1093/biosci/bix025}{oa})
}

\longformpublication{
  T Alex Perkins, \textbf{Carl Boettiger}, Benjamin L. Philips. (2016)
  After the games are over: life-history trade-offs drive dispersal
  attenuation following range expansion. \emph{Ecology and Evolution} 6
  (18) 6425-6434.
  \href{http://dx.doi.org/10.1002/ece3.2314}{doi:10.1002/ece3.2314}.
  (\href{http://oadoi.org/10.1002/ece3.2314}{oa},
  \href{https://github.com/TAlexPerkins/dispersal_tradeoffs}{code})
}

\longformpublication{
  \textbf{Carl Boettiger}, Michael Bode, James N. Sanchirico, Jacob
  LaRiviere, Alan Hastings, and Paul Robert Armsworth (2016). Optimal
  management of a stochastically varying population when policy
  adjustment is costly. \emph{Ecological Applications} 26 (3) 808-817.
  \href{http://dx.doi.org/10.1890/15-0236}{doi:10.1890/15-0236}.
  (\href{http://arxiv.org/pdf/1507.07037v1.pdf}{oa},
  \href{https://github.com/cboettig/pdg_control}{code})
}

\longformpublication{
  \textbf{Carl Boettiger}, Scott Chamberlain, Rutger Vos and Hilmar Lapp
  (2016). RNeXML: a package for reading and writing richly annotated
  phylogenetic, character, and trait data in R. \emph{Methods in Ecology
  and Evolution}.
  \href{http://dx.doi.org/10.1111/2041-210X.12469}{doi:10.1111/2041-210X.12469}.
  (\href{http://arxiv.org/abs/1506.02722}{oa},
  \href{https://github.com/ropensci/RNeXML}{code},
  \href{http://cran.rstudio.com/web/packages/RNeXML}{software})
}

\longformpublication{
  \textbf{Carl Boettiger}, Scott Chamberlain, Edmund Hart, Karthik Ram
  (2015). Building Software, Building Community: Lessons from the
  rOpenSci Project. \emph{Journal of Open Research Software} 3: e8,
  \href{http://dx.doi.org/10.5334/jors.bu}{doi:10.5334/jors.bu}.
}

\longformpublication{
  \textbf{Carl Boettiger} (2015). An introduction to Docker for
  reproducible research. \emph{ACM SIGOPS Operating Systems Review}
  49(1), 71-79.
  \href{http://dx.doi.org/10.1145/2723872.2723882}{doi:10.1145/2723872.2723882}.
  (\href{http://arxiv.org/abs/1410.0846}{oa})
}

\longformpublication{
  \textbf{Carl Boettiger}, Marc Mangel, Stephan Munch (2015). Avoiding
  tipping points in fisheries management through Gaussian process
  dynamic programming. \emph{Proceedings of the Royal Society B}
  282(1801), 8--11.
  \href{http://dx.doi.org/10.1098/rspb.2014.1631}{doi:10.1098/rspb.2014.1631}.
  (\href{http://arxiv.org/abs/1412.8081}{oa},
  \href{https://github.com/cboettig/nonparametric-bayes}{code},
  \href{http://dx.doi.org/10.5061/dryad.mj226}{data})
}

%%%%%

\longformpublication{
  \textbf{Carl Boettiger}, Alan Hastings (2013). No early warning
  signals for stochastic transitions: insights from large deviation
  theory. \emph{Proceedings of the Royal Society B}. \\
  \href{http://dx.doi.org/10.1098/rspb.2013.1372}{doi:10.1098/rspb.2013.1372}.
  (\href{http://arxiv.org/abs/1307.4415}{oa},
  \href{https://github.com/cboettig/prosecutors-fallacy}{code})
}

\longformpublication{
  \textbf{Carl Boettiger}, Noam Ross, Alan Hastings (2013). Early
  warning signals: The charted and uncharted territories.
  \emph{Theoretical Ecology}
  \href{http://dx.doi.org/10.1007/s12080-013-0192-6}{doi:10.1007/s12080-013-0192-6}.
  (\href{http://arxiv.org/abs/1305.6700}{oa},
  \href{https://github.com/cboettig/ews-review}{code})
}

\longformpublication{
  \textbf{Carl Boettiger}, Alan Hastings (2013). Tipping points: From
  patterns to predictions, \emph{Nature} 493, 157--158.
  \href{http://dx.doi.org/10.1038/493157a}{doi:10.1038/493157a}.
}

\longformpublication{
  \textbf{Carl Boettiger}, Alan Hastings (2012). Early Warning Signals
  and the Prosecutor's Fallacy, \emph{Proceedings of the Royal Society
  B} 279 (1748) 4734-4739.
  \href{http://dx.doi.org/10.1098/rspb.2012.2085}{doi:10.1098/rspb.2012.2085}.
  (\href{http://arxiv.org/abs/1210.1204}{oa},
  \href{https://github.com/cboettig/prosecutors-fallacy}{code},
  \href{http://dx.doi.org/10.5061/dryad.2k462}{data})
}

\longformpublication{
  \textbf{Carl Boettiger}, Duncan Temple Lang, Peter Wainwright (2012).
  rfishbase: exploring, manipulating and visualizing FishBase data from
  R, \emph{Journal of Fish Biology}. 81 (6) 2030--2039.
  \href{http://dx.doi.org/10.1111/j.1095-8649.2012.03464.x}{doi:10.1111/j.1095-8649.2012.03464.x}.
  (\href{https://github.com/ropensci/rfishbase/blob/master/inst/doc/rfishbase/rfishbase_github.md}{oa},
  \href{https://github.com/ropensci/rfishbase}{code},
  \href{http://cran.at.r-project.org/web/packages/rfishbase/}{software})
}

\longformpublication{
  \textbf{Carl Boettiger}, Duncan Temple Lang (2012). Treebase: An R
  package for discovery, access and manipulation of online phylogenies,
  \emph{Methods in Ecology and Evolution} 3 (6) 1060--1066.
  \href{http://dx.doi.org/10.1111/j.2041-210X.2012.00247.x}{doi:10.1111/j.2041-210X.2012.00247x}.
  (\href{https://github.com/ropensci/treebase/blob/master/inst/doc/treebase/treebase_github.md}{oa},
  \href{https://github.com/ropensci/treebase}{code},
  \href{http://cran.at.r-project.org/web/packages/treebase/}{software})
}

\longformpublication{
  \textbf{Carl Boettiger}, Alan Hastings (2012). Quantifying Limits to
  Detection of Early Warning for Critical Transitions, \emph{Journal of
  the Royal Society: Interface} 9 (75) 2527-2539.
  \href{http://dx.doi.org/10.1098/rsif.2012.0125}{doi:10.1098/rsif.2012.0125}.
  (\href{http://arxiv.org/abs/1204.6231}{oa},
  \href{https://github.com/cboettig/earlywarning}{code})
}

\longformpublication{
  Jeremy M. Beaulieu, Dwueng-Chwuan Jhwueng, \textbf{Carl Boettiger},
  Brian O'Meara, (2012). Modeling Stabilizing Selection: Expanding the
  Ornstein-Uhlenbeck Model of Adaptive Evolution, \emph{Evolution} 66
  (8) 2369-2383.
  \href{http://dx.doi.org/10.1111/j.1558-5646.2012.01619.x}{doi:10.1111/j.1558-5646.2012.01619.x}
  (\href{http://cran.r-project.org/web/packages/OUwie/index.html}{software})
}

\longformpublication{
  \textbf{Carl Boettiger}, Graham Coop, Peter Ralph (2012). Is your
  phylogeny informative? Measuring the power of comparative methods,
  \emph{Evolution} 66 (7) 2240-51.
  \href{http://dx.doi.org/10.1111/j.1558-5646.2011.01574.x}{doi:10.1111/j.1558-5646.2011.01574.x},
  (\href{http://arxiv.org/abs/1110.4944}{oa},
  \href{https://github.com/cboettig/pmc}{code},
  \href{http://datadryad.org/handle/10255/dryad.37645}{data})
}

\longformpublication{
  \textbf{Carl Boettiger}, Jonathan Dushoff, Joshua S Weitz (2010).
  Fluctuation domains in adaptive evolution, \emph{Theoretical
  Population Biology} 77 (1) 6-13.
  \href{http://dx.doi.org/10.1016/j.tpb.2009.10.003}{doi:10.1016/j.tpb.2009.10.003}.
  (\href{http://arxiv.org/abs/1004.4233}{oa},
  \href{https://github.com/cboettig/fluctuationDomains}{code},
  \href{http://datadryad.org/handle/10255/dryad.37625}{data})
}

\longformpublication{
  James J. Wray, Neta A. Bahcall, Paul Bode, \textbf{Carl Boettiger},
  Phillip Hopkins (2006). The Shape, Multiplicity, and Evolution of
  Superclusters in Lambda-CDM Cosmology, \emph{The Astrophysical
  Journal} 652 (2) 907-916.
  \href{http://dx.doi.org/10.1086/508600}{doi:10.1086/50860}.
  (\href{http://arxiv.org/abs/astro-ph/0603060}{oa})
 }


\section{Book Chapters}

\longformpublication{ \textbf{Carl Boettiger} (2017). A Reproducible R Notebook Using Docker. In J. Kitzes, D. Turek, \& F. Deniz (Eds.), The Practice of
  Reproducible Research: Case Studies and Lessons from the
  Data-Intensive Sciences (1st ed., pp.~109--117). Oakland, CA: UC
  Press. \href{https://www.ucpress.edu/book.php?isbn=9780520294752}{ISBN:9780520294752}}
 

\switchcolumn

\section{Software}

\longformpublication{
  \href{https://github.com/ropensci/emld}{\texttt{emld}}: Ecological
  Metadata as Linked Data. Carl Boettiger (2019).}

\longformpublication{
  \href{https://github.com/ropensci/virtuoso}{\texttt{virtuoso}}:
  Interface to Virtuoso using ODBC. Carl Boettiger (2019).}
\longformpublication{
  \href{https://github.com/ropensci/rdflib}{\texttt{rdflib}}: Tools to
  Manipulate and Query Semantic Data. Carl Boettiger (2018).
}

\longformpublication{
  \href{https://github.com/ropensci/codemetar}{\texttt{codemetar}}:
  Generate CodeMeta Metadata for R Packages. Carl Boettiger, Maëlle
  Salmon (2018).
}

\longformpublication{
  \href{https://github.com/cboettig/EcoNetGen}{\texttt{EcoNetGen}}:
  Simulate and Sample from Ecological Interaction Networks. Marcus de
  Aguiar, Erica Newman, Mathias Pires, Carl Boettiger (2018).
}

\longformpublication{
  \href{https://github.com/ropensci/piggyback/}{\texttt{piggyback}}:
  Managing Larger Data on a GitHub Repository. Carl Boettiger (2018).
}

\longformpublication{
  \href{https://github.com/ropensci/arkdb/}{\texttt{arkdb}}: Archive and
  Unarchive Databases Using Flat Files. Carl Boettiger (2018).
}

\longformpublication{
  \href{https://github.com/ropensci/EML}{\texttt{EML}}: Read and Write
  Ecological Metadata Language File. Carl Boettiger, Matt Jones (2016;
  v2 2019).}

\longformpublication{
  \href{https://github.com/ropensci/RNeXML}{\texttt{RNeXML}}:
  Semantically Rich I/O for the NeXML Phylogenetics Format. Carl
  Boettiger, Scott Chamberlain, Hilmar Lapp, Rutger Voss (2014).}

\longformpublication{
  \href{https://github.com/cboettig/pmc}{\texttt{pmc}}: Phylogenetic
  Monte Carlo. Carl Boettiger (2012).}

\longformpublication{
  \href{https://github.com/cboettig/knitcitations}{\texttt{knitcitations}}:
  Citations for Knitr Markdown Files. Carl Boettiger (2012).
}

\longformpublication{
  \href{https://github.com/ropensci/rfishbase}{\texttt{rfishbase}}: R
  Interface to FishBase. Carl Boettiger, Scott Chamberlain, Duncan
  Temple Lang, Peter Wainwright (2011; v2 2015; v3 2019).}

\longformpublication{
  Carl Boettiger, Dirk Eddelbuettel. \href{https://rocker-project.org}{The Rocker Project}: Docker images
  for the R environment. (Language: Dockerfile)}

\longformpublication{
  Carl Boettiger, Matt Jones, et al. \href{https://codemeta.github.io}{The CodeMeta Project}: Software
  Metadata Exchange. (Language: JSON-LD)
}
\medskip % Extra whitespace before the next section


\section{Service}

  NCEAS \href{https://www.nceas.ucsb.edu/content/nceas-science-advisers}{Scientific
  Advisory Board}. (2014 - Current)\\
  
  rOpenSci \href{https://ropensci.org/about/\#team}{Leadership Team}. (2012 - Current)\\
  
  Jetstream Cloud Computing
  \href{https://jetstream-cloud.org/about/advisory-board.php}{Stakeholder
  Advisory Board}, XSEDE, NSF. (2015 - Current)\\
  
  Reviewer for over 40 journals, NSF review panelist, ad hoc reviewer
  for NSF, NERSC,NERC and UC-CCGA.


%----------------------------------------------------------------------------------------

\end{paracol}

%----------------------------------------------------------------------------------------

\end{document}
