%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
% personal data
\name{Carl}{Boettiger}
\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{my address, line 1, line 2, line 3, postcode}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\address{\textbf{Address:} \\
                 ESPM Department, \\
                 University of California, \\
                 130 Mulford Hall \#3114, \\
                 Berkeley, CA 94720, USA 
         } 



\email{cboettig@berkeley.edu}                               % optional, remove / comment the line if not wanted
\homepage{http://carlboettiger.info}                         % optional, remove / comment the line if not wanted
\extrainfo{twitter: \href{https://twitter.com/cboettig}{@cboettig} \\
           orcid: \href{https://orcid.org/0000-0002-1642-628X}{0000-0002-1642-628X} 

           %\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------


\usepackage{etaremune}
\makeatletter
\long\def\thebibliography#1{%
  \section*{\refname}%
  \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}
  \settowidth{\dimen0}{\@biblabel{#1}}%
  \setlength{\dimen2}{\dimen0}%
  \addtolength{\dimen2}{\labelsep}
  \sloppy
  \clubpenalty 4000 
  \@clubpenalty 
  \clubpenalty 
  \widowpenalty 4000
  \sfcode `\.\@m
  \renewcommand{\labelenumi}{\@biblabel{\theenumi}} % labels like [3], [2], [1]
  \begin{etaremune}[labelwidth=\dimen0,leftmargin=\dimen2]\@openbib@code
}
\def\endthebibliography{\end{etaremune}}
\def\@bibitem#1{%
  \item \if@filesw\immediate\write\@auxout{\string\bibcite{#1}{\the\value{enumi}}}\fi\ignorespaces
}
\makeatother


\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{Undergraduate electrical and electronic engineer completing the final year of a master's degree. Passionate about science, with strong technical, business, and interpersonal skills for working in a team and successfully completing a project.}

\section{Previous Employment}

\section{employment}\label{employment}

\begin{itemize}
\item
  2015 Assistant Professor, Department of
  \href{http://ourenvironment.berkeley.edu}{Environmental Science,
  Policy and Management}, \href{http://www.berkeley.edu}{University of
  California Berkeley}
\item
  2013-2015 NSF Post-doctoral Scholar in the Department of
  \href{https://www.soe.ucsc.edu/departments/applied-mathematics-statistics}{Applied
  Mathematics and Statistics} at the
  \href{http://www.ucsc.edu}{University of California, Santa Cruz}
  Mentors: \href{http://users.soe.ucsc.edu/~msmangel/}{Marc Mangel},
  \href{http://swfsc.noaa.gov/staff.aspx?\&id=17294}{Stephan Munch}
\end{itemize}

\section{education}\label{education}

\begin{itemize}
\item
  2012 Ph.D Population Biology, \href{http://ucdavis.edu}{University of
  California, Davis}. Mentor: \href{http://two.ucdavis.edu/~me}{Alan
  Hastings}
\item
  2007 A.B in Physics \href{http://princeton.edu}{Princeton University},
  with honors and certificates in \emph{biophysics} and \emph{applied
  and computational mathematics.}
\end{itemize}

\section{publications}\label{publications}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  James J. Wray, Neta A. Bahcall, Paul Bode, \textbf{Carl Boettiger},
  Phillip Hopkins. (2006) The Shape, Multiplicity, and Evolution of
  Superclusters in Lambda-CDM Cosmology, \emph{The Astrophysical
  Journal} 652 (2) 907-916.
  \href{http://dx.doi.org/10.1086/508600}{doi}:10.1086/508600
  (\href{http://arxiv.org/abs/astro-ph/0603060}{preprint})
\item
  \textbf{Carl Boettiger}, Jonathan Dushoff, Joshua S Weitz (2010)
  Fluctuation domains in adaptive evolution, \emph{Theoretical
  Population Biology} 77 (1) 6-13.
  \href{http://dx.doi.org/10.1016/j.tpb.2009.10.003}{doi}:10.1016/j.tpb.2009.10.003
  (\href{http://arxiv.org/abs/1004.4233}{preprint})
  (\href{https://github.com/cboettig/fluctuationDomains}{code})
  (\href{http://datadryad.org/handle/10255/dryad.37625}{data})
\item
  \textbf{Carl Boettiger}, Graham Coop, Peter Ralph (2012) Is your
  phylogeny informative? Measuring the power of comparative methods,
  \emph{Evolution} 66 (7) 2240-51.
  \href{http://dx.doi.org/10.1111/j.1558-5646.2011.01574.x}{doi}:10.1111/j.1558-5646.2011.01574.x
  (\href{http://arxiv.org/abs/1110.4944}{preprint})
  (\href{https://github.com/cboettig/pmc}{code})
  (\href{http://datadryad.org/handle/10255/dryad.37645}{data})
\item
  Jeremy M. Beaulieu, Dwueng-Chwuan Jhwueng, \textbf{Carl Boettiger} and
  Brian O'Meara, (2012). Modeling Stabilizing Selection: Expanding the
  Ornstein-Uhlenbeck Model of Adaptive Evolution, \emph{Evolution} 66
  (8) 2369-2383.
  \href{http://dx.doi.org/10.1111/j.1558-5646.2012.01619.x}{doi}:10.1111/j.1558-5646.2012.01619.x
  (\href{http://cran.r-project.org/web/packages/OUwie/index.html}{software})
\item
  \textbf{Carl Boettiger} and Alan Hastings (2012). Quantifying Limits
  to Detection of Early Warning for Critical Transitions, \emph{Journal
  of the Royal Society: Interface} 9 (75) 2527-2539.
  \href{http://dx.doi.org/10.1098/rsif.2012.0125}{doi}:10.1098/rsif.2012.0125
  (\href{http://arxiv.org/abs/1204.6231}{preprint})
  (\href{https://github.com/cboettig/earlywarning}{code})
\item
  \textbf{Carl Boettiger}, Duncan Temple Lang (2012). Treebase: An R
  package for discovery, access and manipulation of online phylogenies,
  \emph{Methods in Ecology and Evolution} 3 (6) 1060--1066.
  \href{http://dx.doi.org/10.1111/j.2041-210X.2012.00247.x}{doi}:10.1111/j.2041-210X.2012.00247.x
  (\href{https://github.com/ropensci/treebase/blob/master/inst/doc/treebase/treebase_github.md}{preprint})
  (\href{https://github.com/ropensci/treebase}{code})
  (\href{http://cran.at.r-project.org/web/packages/treebase/}{software})
\item
  \textbf{Carl Boettiger}, Duncan Temple Lang, Peter Wainwright (2012).
  rfishbase: exploring, manipulating and visualizing FishBase data from
  R, \emph{Journal of Fish Biology}. 81 (6) 2030--2039.
  \href{http://dx.doi.org/10.1111/j.1095-8649.2012.03464.x}{doi}:10.1111/j.1095-8649.2012.03464.x
  (\href{https://github.com/ropensci/rfishbase/blob/master/inst/doc/rfishbase/rfishbase_github.md}{preprint})
  (\href{https://github.com/ropensci/rfishbase}{code})
  (\href{http://cran.at.r-project.org/web/packages/rfishbase/}{software})
\item
  \textbf{Carl Boettiger}, Alan Hastings (2012). Early Warning Signals
  and the Prosecutor's Fallacy, \emph{Proceedings of the Royal Society
  B} 279 (1748) 4734-4739.
  \href{http://dx.doi.org/10.1098/rspb.2012.2085}{doi}:10.1098/rspb.2012.2085
  (\href{http://arxiv.org/abs/1210.1204}{preprint})
  (\href{https://github.com/cboettig/prosecutors-fallacy}{code})
  (\href{http://dx.doi.org/10.5061/dryad.2k462}{data})
\item
  \textbf{Carl Boettiger}, Alan Hastings (2013). Tipping points: From
  patterns to predictions, \emph{Nature} 493, 157--158.
  \href{http://dx.doi.org/10.1038/493157a}{doi}:10.1038/493157a
\item
  \textbf{Carl Boettiger}*, Noam Ross*, Alan Hastings. (2013) Early
  warning signals: The charted and uncharted territories.
  \emph{Theoretical Ecology}
  \href{http://dx.doi.org/10.1007/s12080-013-0192-6}{doi}:10.1007/s12080-013-0192-6
  (\href{http://arxiv.org/abs/1305.6700}{preprint})
  (\href{https://github.com/cboettig/ews-review}{code})
\item
  \textbf{Carl Boettiger}, Alan Hastings. (2013) No early warning
  signals for stochastic transitions: insights from large deviation
  theory. \emph{Proceedings of the Royal Society B}.
  \href{http://dx.doi.org/10.1098/rspb.2013.1372}{doi}:10.1098/rspb.2013.1372
  (\href{http://arxiv.org/abs/1307.4415}{preprint})
  (\href{https://github.com/cboettig/prosecutors-fallacy}{code})
\item
  \textbf{Carl Boettiger}, Marc Mangel, Stephan Munch. (2015) Avoiding
  tipping points in fisheries management through Gaussian process
  dynamic programming. \emph{Proceedings of the Royal Society B}
  282(1801), 8--11.
  \href{http://dx.doi.org/10.1098/rspb.2014.1631}{doi}:10.1098/rspb.2014.1631
  (\href{http://arxiv.org/abs/1412.8081}{preprint})
  (\href{https://github.com/cboettig/nonparametric-bayes}{code})
  (\href{http://dx.doi.org/10.5061/dryad.mj226}{data})
\item
  \textbf{Carl Boettiger}. (2015) An introduction to Docker for
  reproducible research. ACM SIGOPS Operating Systems Review, Special
  Issue on Repeatability and Sharing of Experimental Artifacts. 49(1),
  71-79.
  \href{http://dx.doi.org/10.1145/2723872.2723882}{doi}:10.1145/2723872.2723882
  (\href{http://arxiv.org/abs/1410.0846}{preprint})
\item
  \textbf{Carl Boettiger}, Scott Chamberlain, Rutger Vos and Hilmar
  Lapp. (2015) RNeXML: a package for reading and writing richly
  annotated phylogenetic, character, and trait data in R. Methods in
  Ecology and Evolution.
  \href{http://dx.doi.org/10.1111/2041-210X.12469}{doi}:10.1111/2041-210X.12469
  (\href{http://arxiv.org/abs/1506.02722}{arxiv})
  (\href{https://github.com/ropensci/RNeXML}{code})
  (\href{http://cran.rstudio.com/web/packages/RNeXML}{software})
\item
  \textbf{Carl Boettiger}, Scott Chamberlain, Edmund Hart, Karthik Ram.
  (2015) Building Software, Building Community: Lessons from the
  rOpenSci Project. \emph{Journal of Open Research Software} 3: e8,
  \href{http://dx.doi.org/10.5334/jors.bu}{doi}:10.5334/jors.bu
\item
  \textbf{Carl Boettiger}, Michael Bode, James N. Sanchirico, Jacob
  LaRiviere, Alan Hastings, and Paul Robert Armsworth. (2015) Optimal
  management of a stochastically varying population when policy
  adjustment is costly. \emph{Ecological Applications} 26 (3) 808-817.
  \href{http://dx.doi.org/10.1890/15-0236}{doi}:10.1890/15-0236
  (\href{http://arxiv.org/pdf/1507.07037v1.pdf}{preprint})
  (\href{https://github.com/cboettig/pdg_control}{code})
\end{enumerate}

\section{grants}\label{grants}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Computational Science Graduate Fellowship (2008). Department of
  Energy, \#DE-FG02-97ER25308, 149,000 USD.
  (\href{https://dx.doi.org/10.6084/m9.figshare.2010246}{proposal})
\item
  IIASA YSSP fellowship (2009). National Academy of Sciences,
  OISE-0738129, 8,000 USD.
  (\href{http://doi.org/10.6084/m9.figshare.678310}{proposal})
\item
  Supercomputing grant (2011). DOE \#DE-AC02-05CH11231. 50,000hrs.
\item
  \href{http://ropensci.org}{rOpenSci Project} (2013, Co-PI). Alfred P.
  Sloan Foundation 180,000 USD.
\item
  \href{http://www.nsf.gov/pubs/2012/nsf12497/nsf12497.htm}{NSF Biology
  Post-doc} (2013). NSF
  \href{http://www.nsf.gov/awardsearch/showAward?AWD_ID=1306697}{\#DBI-1306697},
  138,000 USD.
  (\href{http://doi.org/10.6084/m9.figshare.652970}{proposal})
\item
  \href{http://ropensci.org}{rOpenSci Project}, phase II. (2014, Co-PI).
  Alfred P. Sloan Foundation 300,000 USD.
\item
  Codemeta project (2015). NSF EAGER,
  \href{https://www.nsf.gov/awardsearch/showAward?AWD_ID=1549758}{\#1549758}
  165,782 USD.
  (\href{https://dx.doi.org/10.6084/m9.figshare.2055972}{proposal})
\item
  \href{http://ropensci.org}{rOpenSci Project} (2015-2018, Co-PI).
  Helmsley Trust 2,900,000 USD.
\end{enumerate}

\section{invited talks}\label{invited-talks}

\subsection{2015}\label{section}

\begin{itemize}
\tightlist
\item
  \href{http://ecows.oc.ntu.edu.tw/itnlws/}{Empirical Dynamical Modeling
  and Forecasting in Nonlinear Systems}, NTU, Taiwan.
\end{itemize}

\subsection{2014}\label{section-1}

\begin{itemize}
\tightlist
\item
  Berkeley Initiative for Global Change Biology (student organized), UC
  Berkeley, CA.
\item
  \href{http://dimacs.rutgers.edu/Workshops/GlobalChange/announcement.html}{DIMACS}
  Global Change, Berkeley CA.
\item
  Zoology Seminar, University of Wisconsin, Madison, WI.
\item
  ESPM Seminar, UC Berkeley, CA.
\end{itemize}

\subsection{2013 \& prior}\label{prior}

\begin{itemize}
\tightlist
\item
  MBI speaker,
  \href{http://www.mbi.ohio-state.edu/2013/ws3description.html}{Sustainable
  Management of Living Natural Resources}, Columbus, OH.
\item
  WHOI Seminar speaker, Woods Hole, MA.
\item
  UC Davis Dept of Environmental Resources and Economics; Davis, CA.
\item
  SSB Symposium speaker, Evolution Conference, Ottawa, CAN.
\end{itemize}

\section{invited workshops}\label{invited-workshops}

\subsection{2016}\label{section-2}

\begin{itemize}
\tightlist
\item
  \href{http://sched.co/5wK5}{Force16 Codemeta Workshop}, Portland OR
  (organizer)
\item
  \href{https://codemeta.github.io}{CodeMeta NSF Workshop} Portland, OR
  (organizer)
\item
  \href{http://unconf16.ropensci.org}{rOpenSci unconference}, San
  Francisco, CA
\end{itemize}

\subsection{2015}\label{section-3}

\begin{itemize}
\tightlist
\item
  Moore-Sloan Data Science Environments: Second Annual Data Science
  Summit
\item
  \href{https://github.com/NCEAS/ds-workshop-2015}{Data Intensive
  Training Workshop}, NCEAS, Santa Barbara, CA
\item
  \href{http://www.nsf.gov/pubs/2015/nsf15562/nsf15562.htm}{NSF Big Data
  Hubs} Design Charette, Western Region.
\item
  \href{http://unconf.ropensci.org/}{rOpenSci unconference}, San
  Fransisco CA.
\item
  PDGC Workshop, NIMBIOS, Knoxville TN
\end{itemize}

\subsection{2014}\label{section-4}

\begin{itemize}
\tightlist
\item
  \href{http://ropensci.org/blog/2014/05/14/ropenhack/}{rOpenSci
  unconference}, San Fransisco CA.
\item
  \href{https://github.com/Reproducible-Science-Curriculum/Reproducible-Science-Hackathon-Dec-08-2014}{Reproducible
  Science: Curriculum \& Workflow}, NESCent, Durham, NC.
\item
  \href{http://wssspe.researchcomputing.org.uk/wssspe2/}{WSSSPE 2.0}.
  New Orleans, LA.
\item
  Workflows Working Group, NCEAS, Santa Barbara, CA.
\end{itemize}

\subsection{2013 \& prior}\label{prior-1}

\begin{itemize}
\tightlist
\item
  \href{http://www.mbi.ohio-state.edu/2013/ws3description.html}{Sustainable
  Management of Living Natural Resources}, MBI Columbus, OH.
\item
  Academic software \& workforce development,
  \href{http://isees.nceas.ucsb.edu}{ISEES}. Oakland, CA.
\item
  Software Lifecycle, \href{http://isees.nceas.ucsb.edu}{ISEES}, Santa
  Barbara, CA.
\item
  \href{http://www.nimbios.org/workinggroups/WG_PDG}{Pretty Darn Good
  Control}, NIMBIOS, Knoxville, TN
\item
  \href{http://www.aimath.org/WWN/populationmodel/}{Stochastic spatial
  modeling in population dynamics}, AIM, Palo Alto, CA.
\end{itemize}

\section{awards}\label{awards}

\begin{itemize}
\tightlist
\item
  2011 \emph{Volterra Award} (Best student talk, ESA Theory Section)
\item
  2007 Elected to Membership in the Society of \emph{Sigma Xi}
\item
  2007 Allen G. Shenstone Prize in Physics, Princeton University
\item
  2007 The Class of 1870 Old English Prize, Princeton University
\item
  2006 Kusaka Memorial Prize in Physics, Princeton University
\item
  2006 Plasma Physics Fellow, PPPL
\end{itemize}

\section{service}\label{service}

\subsection{national}\label{national}

\begin{itemize}
\tightlist
\item
  NCEAS Scientific Advisory
  \href{https://www.nceas.ucsb.edu/news/nceas-appoints-new-science-advisers}{Board}
\item
  \href{http://ropensci.org/about/\#leadership}{rOpenSci Leadership
  team}
\item
  Jestream NSF cloud computing Stakeholder Advisory Board
\end{itemize}

\subsection{campus}\label{campus}

\begin{itemize}
\tightlist
\item
  UC Berkeley, Berkeley Research Computing Advisory Committee
\end{itemize}

\subsection{reviewer for:}\label{reviewer-for}

\begin{itemize}
\item
  \textbf{2015} Proceedings of the National Academy of Sciences, Journal
  of Statistical Software, Bioinformatics, Chapman \& Hall, Ecology
  Letters, Ecology, PeerJ, F1000 Research, Journal of Librarianship \&
  Scholarly Communication, Nature Communications, Theoretical Ecology,
  Trends in Ecology \& Evolution, Grid Computing
\item
  \textbf{2014} Theoretical Ecology, Biodiversity Data Journal, Ecology
  Letters, Journal of Theoretical Biology, American Naturalist,
  Proceedings of the National Academy of Sciences, Proceedings of the
  Royal Society B
\item
  \textbf{2013} Theoretical Ecology, Francis \& Taylor, Ideas in Ecology
  and Evolution, The R Journal, National Science Foundation, Proceedings
  of the Royal Society B, Journal of Open Research Software, Canadian
  Journal of Fisheries and Aquatic Sciences
\item
  \textbf{2012} Theoretical Ecology, Evolution, Methods in Ecology and
  Evolution, Proceedings of the Royal Society B, PLoS ONE, Ecology,
  Conservation Letters, Ecology Letters
\item
  \textbf{2011} Theoretical Ecology, Ecological Modelling, Evolution,
  Methods in Ecology and Evolution, Ecosphere
\item
  \textbf{2010 \& prior} Theoretical Ecology, Journal of Mathematical
  Biology, Ecological Modelling, Ecology
\end{itemize}

\section{selected software}\label{selected-software}

\begin{itemize}
\tightlist
\item
  Carl Boettiger, Scott Chamberlain, Rutger Vos and Hilmar Lapp. (2015)
  RNeXML: a package for reading and writing richly annotated
  phylogenetic, character, and trait data in R. On
  \href{https://cran.rstudio.com/web/packages/RNeXML/}{software}
\item
  Carl Boettiger (2013). knitcitations: Dynamic citations for dynamic
  documents. On
  \href{http://cran.r-project.org/web/packages/knitcitations/}{software}.
\item
  Carl Boettiger, Scott Chamberlain, Karthik Ram, Edmund Hart (2013).
  rfigshare: Programmatic access to the figshare data repository. On
  \href{http://cran.r-project.org/web/packages/rfigshare/}{software}.
\item
  Carl Boettiger (2012). pmc: Phylogenetic Monte Carlo. On
  \href{https://cran.rstudio.com/web/packages/pmc/}{software}.
\item
  Carl Boettiger \& Duncan Temple Lang (2011). treebase: An R interface
  to TreeBASE. On
  \href{http://cran.r-project.org/web/packages/treebase/}{software}.
\item
  Carl Boettiger (2011). rfishbase: Programmatic access to FishBase. On
  \href{http://cran.r-project.org/web/packages/rfishbase/}{software}.
\end{itemize}

I am also a founding member of the \href{http://ropensci.org}{rOpenSci
project}. My software impact is also measured relative to other
academics by \href{http://depsy.org/person/329935}{depsy.org}

\section{theses}\label{theses}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Carl Boettiger, David Huse (2006) Clonal Interference Models in
  Population Genetics. \emph{Princeton Physics Dept}.
  \href{http://dx.doi.org/10.6084/m9.figshare.678305}{doi}:10.6084/m9.figshare.678305
\item
  Carl Boettiger, Joshua Weitz, Simon Levin (2007) Adaptive Dynamics:
  Branching Phenomena and the Canonical Equation \emph{Princeton Physics
  Dept}.
  \href{http://dx.doi.org/10.6084/m9.figshare.678306}{doi}:10.6084/m9.figshare.678306
\item
  Carl Boettiger, Stephen Pacala, David Huse (2007) Ensemble Behavior
  from Individual Dynamics in Multispecies Forest Populations.
  \emph{Princeton Physics Dept}.
  \href{http://dx.doi.org/10.6084/m9.figshare.678304}{doi}:10.6084/m9.figshare.678304
\item
  Carl Boettiger (2012). Regime shifts in ecology and evolution (PhD
  Dissertation).
  \href{http://dx.doi.org/10.6084/m9.figshare.97218}{doi}:10.6084/m9.figshare.97218
\end{enumerate}

\section{media interviews}\label{media-interviews}

\begin{itemize}
\tightlist
\item
  Tachibana, C. (2014). ``The paperless lab'' \emph{Science} 345(6195)
  pp.~468-470.
  \href{http://www.sciencemag.org/site/products/lst_20140613.xhtml}{10.1126/science.opms.p1400087}
\item
  Mascarelli, A. (2014) ``Research tools: Jump off the page.''
  \emph{Nature} 507, 523--525.
  \href{http://dx.doi.org/10.1038/nj7493-523a}{doi}:10.1038/nj7493-523a
\item
  Check Hayden E (2013). ``Mozilla Plan Seeks to Debug Scientific
  Code.'' \emph{Nature}, 501, pp.~472-472.
  \href{http://dx.doi.org/10.1038/501472a}{doi}:10.1038/501472a
\item
  Van Noorden R (2013). ``Data-Sharing: Everything on Display.''
  \emph{Nature}, 500, pp.~243-245.
  \href{http://dx.doi.org/10.1038/nj7461-243a}{doi}:10.1038/nj7461-243a
\item
  Gewin, Virginia (2013). ``Turning Point: Carl Boettiger''
  \emph{Nature}, 493 p 711
  \href{http://dx.doi.org/10.1038/nj7434-711a}{doi}:10.1038/nj7434-711a
\item
  Wald, Chelsea (2010). ``Scientists Embrace Openness'' \emph{Science}.
  \href{http://dx.doi.org/10.1126/science.caredit.a1000036}{doi}:10.1126/science.caredit.a1000036
\end{itemize}

\end{document}


%% end of file `template.tex'.


