\documentclass[margin]{res}
%\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage{palatcm}
\usepackage{palatino}
\usepackage{newcent}
\usepackage{times}
\usepackage{microtype}
\usepackage[colorlinks]{hyperref}
\usepackage{etaremune}

\hypersetup{
unicode=false,          % non-Latin characters in Acrobat’s bookmarks
pdftoolbar=false,        % show Acrobat’s toolbar?
pdfmenubar=false,        % show Acrobat’s menu?
pdffitwindow=false,     % window fit to page when opened
pdfstartview={FitH},    % fits the width of the page to the window
pdftitle={Carl Boettiger - Vita},    % title
pdfauthor={Carl Boettiger},     % author
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links
citecolor=blue,        % color of links to bibliography
filecolor=blue,      % color of file links
urlcolor=blue           % color of external links
}

\newsectionwidth{7em}
\renewcommand{\sectionfont}[1]{\bf#1}
% want the document to start higher?
%\voffset = -.5in
% also modify text height...defaults to 9 in  %larger number means more text per page!
\textheight 9.2in

\usepackage{fancyhdr}
\pagestyle{fancyplain}
%\fancyhf{}
%\rhead{ \fancyplain{}{\thepage} }
\renewcommand{\headrulewidth}{0pt}
\cfoot{\fancyplain{}{\thepage} }
\rfoot{\fancyplain{}{Boettiger}}

\name{Carl Boettiger}
%\address{Center for Population Biology, \\ 1 Shields Avenue\\University of California, Davis \\ Davis, CA 96516}
\address{\textbf{Work:} \\
                 110 Shaffer Rd \\ 
                 Santa Cruz, CA 95050, USA \\
                 cboettig@soe.ucsc.edu  \\
                 http://carlboettiger.info
        } 
\address{\textbf{Home:} \\
                 2534 Bombadil Lane \\ 
                 Davis CA 95616, USA \\ 
                 cboettig@gmail.com
        }


\begin{document}
\begin{resume}

\section{Employment}
\begin{format}
\title{l}\location{r}\\\dates{r}\\
\body\\
\end{format}

\title{\textbf{University of California, Santa Cruz}}\location{Santa Cruz, CA 95064}\dates{10/15/2012 - Present}
\begin{position}
NSF Postdoctoral Researcher \\
Mentors: Marc Mangel \& Stephan Munch 
\end{position}

\section{Education}
\begin{format}
\title{l}\location{r}\\\dates{r}\\
\body\\
\end{format}

\title{\textbf{University of California, Davis}}\location{Davis, CA 95616}\dates{Ph.D. 09/18/2012}
\begin{position}
Ph.D Population Biology \\
%Completed Sept 18 2012, Awarded Dec 14 2012. \\
Mentor: Alan Hastings
\end{position}

\title{\textbf{Princeton University}}\location{Princeton, NJ 08544}\dates{06/2007}
\begin{position}
A.B  in Physics with Honors \\ 
Certificate in Biophysics; Certificate in Applied and Computational Mathematics\\
Mentors: Stephen Pacala, Simon Levin, David Huse
\end{position}

\section{Publications}

\begin{etaremune}[start = 11]
\item  Boettiger, C., Hastings, A. (2013) ``No early warning signals for stochastic transitions: insights from large deviation theory.'' {\it Proceedings of the Royal Society B}. \href{http://doi.org/10.1098/rspb.2013.1372}{doi:10.1098/rspb.2013.1372}
\item  Boettiger, C.$^*$, Ross, N.$^*$, Hastings, A. (2013) ``Early warning signals: The charted and uncharted territories.'' {\it Theoretical Ecology} \href{http://doi.org/10.1007/s12080-013-0192-6}{doi:10.1007/s12080-013-0192-6}
\item  Boettiger, C., Hastings, A. (2013) ``Tipping points: From patterns to predictions.'' {\it Nature}. 493, 157-158. \href{http://dx.doi.org/10.1038/493157a}{doi:10.1038/493157a}
\item Boettiger, C., Hastings, A. (2012) ``Early Warning Signals and the Prosecutor's Fallacy.'' {\it Proceedings of the Royal Society B}. 279(1748) 4734-4739.   \href{http://dx.doi.org/10.1098/rspb.2012.2085}{doi: 10.1098/rspb.2012.2085}
\item Boettiger, C., Temple-Lang, D., Wainwright, P.C. (2012) ``rfishbase: exploring, manipulating and visualizing FishBase data from R'' {\it Journal of Fish Biology}. 81(6) 2030-2039. \href{http://dx.doi.org/10.1111/j.1095-8649.2012.03464.x}{doi: 10.1111/j.1095-8649.2012.03464.x}
\item Boettiger, C., Temple-Lang, D. (2012)  ``Programmatic access to TreeBASE phylogenies in R.'' {\it Methods in Ecology and Evolution}  \href{http://dx.doi.org/10.1111/j.2041-210X.2012.00247.x}{doi: 10.1111/j.2041-210X.2012.00247.x}
\item Boettiger, C. Hastings, A (2012) ``Quantifying limits to detection of early warning for critical transitions.'' {\it Journal of The Royal Society Interface},  9(75), 2527-2539. \href{http://dx.doi.org/10.1098/rsif.2012.0125}{doi: 10.1098/rsif.2012.0125}.
\item Beaulieu, J.M., Jhwueng, D., Boettiger, C., O'Meara, B. (2012) ``Modeling Stabilizing Selection: Expanding the Ornstein-Uhlenbeck Model of Adaptive Evolution,'' {\it Evolution}. 66(8) 2369-2383. \href{http://dx.doi.org/10.1111/j.1558-5646.2012.01619.x}{doi: 10.1111/j.1558-5646.2012.01619.x)}
\item Boettiger, C., Coop, G,. Ralph, P. (2012) ``Is your phylogeny informative? Measuring the power of comparative methods.'' {\it Evolution}. 66(7) 2240-51. \href{http://dx.doi.org/10.1111/j.1558-5646.2012.01574.x}{doi: 10.1111/j.1558-5646.2012.01574.x}
\item Boettiger, C., Dushoff, J., Weitz, J. S. (2010) ``Variation in the phenotypic dynamics of evolving populations,'' {\it Theoretical Population Biology} 77, 6-13. \href{http://dx.doi.org/10.1016/j.tpb.2009.10.003}{doi: 10.1016/j.tpb.2009.10.003}
\item Wray, J., Bahcall, N., Bode, P., Boettiger, C., Hopkins, P.  (2006)  ``The Shape, Multiplicity, and Evolution of Superclusters in $\Lambda$ CDM Cosmology.''  {\it Astrophysical Journal} 652, 907. \href{http://dx.doi.org/10.1086/508600}{doi: 10.1086/508600}
\end{etaremune}
{ \footnotesize $^*$ denotes equal contribution.}

\section{Submitted or in preparation}


\begin{itemize} %\begin{etaremune}[start = 1]
\item  Boettiger, C., Mangel, M., Munch, S. ``Avoiding tipping points in ecological systems: a Bayesian non-parametric approach to decision making.'' % For {\it Ecology Letters}. 

\item Boettiger, C., Lapp, H., Chamberlain, S., Vos, R. ``RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R'' % For {\it Methods in Ecology and Evolution}

\item Boettiger, C., Temple-Lang, D., Ram, K., Jones, M. ``One simple way to share your data: automated generation and parsing of the Ecological Metadata Langauge for R''   % For {\it Methods in Ecology and Evolution}

\end{itemize} %\end{etaremune}


\section{Presentations} 
\section{\textnormal{2014}}
\emph{Zoology seminar, U Wisconsin-Madison, \textbf{invited speaker}}
\emph{American Society of Naturalists} Asilomar, CA \\ 
\section{\textnormal{2013}}
  \emph{Ecological Society of America} Minneapolis, MN \\ 
  \emph{WHOI}; Cape Cod, MA \textbf{invited speaker}.\\
  UC Davis Dept of Envir Resources and Econ; Davis, CA \textbf{invited speaker}.\\
\section{\textnormal{2012}}
  \emph{Ecological Society of America} Portland, OR. \\ 
  \emph{Evolution}; Ottawa, CAN. SSB Symposium \textbf{invited speaker}.\\
  \emph{iEvoBio}; Ottawa, CAN. \\
  \emph{Computational Science}; Washington DC. 
\section{\textnormal{2011}}
  \emph{Ecological Society of America}; Austin, TX. \\
  \emph{Evolution}; Norman, OK. \\
  \emph{iEvoBio}; Norman, OK. \\
  \emph{Science Online}; Durham, NC.\\
  \emph{Society for Integrative and Comparative Biology.} Salt Lake City, UT. \\
 \section{\textnormal{2010/2009}}
  \emph{iEvoBio}; Portland, OR. 2010 \\
  \emph{Evolution}; Portland OR. 2010 \\
 \emph{University of Tennessee}, Knoxville, TN. 2009 \\
 \emph{IIASA}, Vienna; Austria. 2009


\section{Invited Workshops}
\begin{format}
\title{l}\dates{r} \\
\body
\end{format}

\title{NCEAS Working Group}\dates{2014}
\begin{position}
A toolbox for analysis of long-term ecological dynamics using the Kepler Workflow System
\vspace{-.25cm}
\end{position}


\title{Mathematical Biology Institute (MBI), Columbus, OH}\dates{2013}
\begin{position}
\href{http://www.mbi.ohio-state.edu/2013/ws3description.html}{Sustainable Management of Living Natural Resources} Columbus, OH.  
\vspace{-.25cm}
\end{position}

\title{Planning workshops for an NSF software sustainability center}\dates{2013}
\begin{position}
\href{http://isees.nceas.ucsb.edu}{Institute for Sustainable Earth and Environmental Software}. Mtgs in Oakland CA and Santa Barbara, CA
\vspace{-.25cm}
\end{position}



\title{NIMBioS working group }\dates{2011-13}
\begin{position}
\href{http://www.nimbios.org/workinggroups/WG_PDG}{Pretty Darn Good Control}, Knoxville, TN  
\vspace{-.25cm}
\end{position}

\title{American Institute for Mathematics}\dates{2011}
\begin{position}
 \href{http://www.aimath.org/WWN/populationmodel}{Stochastic and deterministic spatial modeling in population dynamics}, Palo Alto, CA  \vspace{-.25cm}
\end{position}

 
\section{Grants}
\begin{format}
\title{l}\dates{r} \\
\body
\end{format}

\title{\textbf{NSF} Mathematical Biology Postdoctoral Scholar}\dates{2013-15}
\begin{position}
  Management for an uncertain world: robust decision theory in face \\
  of regime shifts Grant No:  DBI-1306697 (\$138,000)
  \vspace{-.25cm}
\end{position}

\title{Co-PI on \textbf{Alfred P. Sloan Foundation} Grant}
\begin{position}
  For work on the \href{http://ropensci.org}{rOpenSci Project}  (\$180,000)
  \vspace{-.25cm}
\end{position}

\title{PI 50,000 hrs \textbf{DOE} supercomputing time}\dates{2011, renewed 2012}
\begin{position} 
  NERSC center, Department of Energy, Grant No. DE-AC02-05CH11231
  \vspace{-.25cm}
\end{position}

\title{\textbf{IIASA} YSSP fellowship}\dates{2009}
\begin{position} 
  award from the National Academy of Sciences, \textbf{NSF} Grant No. OISE-0738129, (\$8,000)
  \vspace{-.25cm}
\end{position}

\title{\textbf{DOE} Computational Science Graduate Fellowship}\dates{2008-2012}
\begin{position} 
  Department of Energy, Grant No: DE-FG02-97ER25308, (\$144,000)
  \vspace{-.25cm}
\end{position}


\section{Honors \& \\ Awards}
\begin{format}
\title{l}\dates{r}\\
\body
\end{format}

\title{\emph{ASN Speaker Award} (Best post-doctoral talk at ASN meeting)}\dates{2014}
\begin{position} \vspace{-.8cm} \end{position}

\title{\emph{Volterra Award} (Best student talk, ESA Theory)}\dates{2011}
\begin{position} \vspace{-.8cm} \end{position}

\title{\emph{Mendeley \& PLoS software competition}, \$1,000}\dates{2011}
\begin{position} \vspace{-.8cm} \end{position}

\title{Elected to Membership in the Society of \emph{Sigma Xi}}\dates{2007}
\begin{position}   \vspace{-.8cm} \end{position}

\title{\emph{Allen G. Shenstone Prize in Physics}, Princeton}\dates{2007}
\begin{position}   \vspace{-.8cm} \end{position}

\title{\emph{The Class of 1870 Old English Prize},  Princeton}\dates{2007}
\begin{position}   \vspace{-.8cm} \end{position}

\title{\emph{Kusaka Memorial Prize in Physics}, Princeton}\dates{2006}
\begin{position}   \vspace{-.8cm} \end{position}

\title{\emph{Plasma Physics Fellow},  PPPL }\dates{2006}
\begin{position}   \vspace{-.8cm} \end{position}



  
  \section{Authored Software (selected)} 
{ \footnotesize
\texttt{RNeXML}: The semantically rich, next generation phylogenetic standard (NeXML) for R (2013) \\
\texttt{reml}: Interpret, generate and publish Ecological Metadata (EML) files (2013) \\
\texttt{wrightscape}: Infer adaptive landscapes from phylogenetic trees (2012) \\
\texttt{knitcitations}: Dynamic citation manager for R. (2012) \\
\texttt{pmc}: Phylogenetic Monte Carlo tools to quantify uncertainty in comparative methods. (2011)\\
\texttt{treeBASE}: An R interface to the TreeBASE API (2011) \\
\texttt{rfishbase}: An R interface to the fishbase database (2011) \\
\texttt{BranchingTime}: Individual based simulations for adaptive dynamics. (2011) \\
\texttt{populationdynamics}: Gillespie algorithms for exact simulation of common ecological models (2011) \\ 
More software at \href{http://github.com/cboettig}{github.com/cboettig} and \href{http://github.com/ropensci}{github.com/ropensci} 
}

\section{Reviewer for:}

\section{\textnormal{2014}}
\emph{Proceedings of the Royal Society B}, \emph{Ecology Letters}, \emph{Pensoft Biodiversity Data Journal}, \emph{Theoretical Ecology}, emph{Journal of Theoretical Biology}

\section{\textnormal{2013}}
\emph{Theoretical Ecology}, \emph{Francis \& Taylor}, \emph{Ideas in Ecology and Evolution}, \emph{The R Journal}, \emph{National Science Foundation}, \emph{Proceedings of the Royal Society B}, \emph{Journal of Open Research Software}, \emph{Canadian Journal of Fisheries and Aquatic Sciences} 

\section{\textnormal{2012}}
\emph{Theoretical Ecology}, \emph{Evolution}, \emph{Methods in Ecology and Evolution}, \emph{Proceedings of the Royal Society B}, \emph{PLoS ONE}, \emph{Ecology}, \emph{Conservation Letters}, \emph{Ecology Letters} 

\section{\textnormal{2011}}
\emph{Theoretical Ecology}, \emph{Ecological Modelling}, \emph{Evolution}, \emph{Methods in Ecology and Evolution}, \emph{Ecosphere}, 

\section{\textnormal{2010 \& prior}}
\emph{Theoretical Ecology}, \emph{Journal of Mathematical Biology}, \emph{Ecological Modelling}, \emph{Ecology}

\section{Other Service:} 
\begin{format}
\title{l}\dates{r}\\
\body 
\end{format}

\title{Student  member for the CBS Dean search.}\dates{2011}
\begin{position} \vspace{-.8cm} \end{position}
\title{Co-chaired the student group on Open Science}\dates{2010-12}
\begin{position} \vspace{-.8cm} \end{position}
\title{Co-chaired the Graduate Teaching Community}\dates{2009-10}
\begin{position} \vspace{-.8cm} \end{position}
\title{Student member for the CPB program review.}\dates{2010}
\begin{position} \vspace{0cm} \end{position}


\section{Teaching\\Experience}
\begin{format}
\title{l}\dates{r}\\
\body
\end{format}

\title{ESA Workshop Instructor}
\dates{Aug 2012}
\begin{position} \vspace{-.8cm} \end{position}
\title{Mentor for Google Summer of Code, R-Project}
\dates{Summer 2012}
\begin{position} \vspace{-.8cm} \end{position}
\title{Instructor, Bodega Phylogenetics Workshop}
\dates{Winter 2011}
\begin{position} \vspace{-.8cm} \end{position}
\title{Student Mentor, CLIMB program}
\dates{Spring, Summer 2008}
\begin{position} \vspace{-.8cm} \end{position}
\title{Teaching Assistant: Introductory Zoology}
\dates{Winter 2008} \begin{position} \vspace{-.0cm} \end{position}




\section{Interviews}

Mascarelli, A. (2014) ``Research tools: Jump off the page.'' \textbf{Nature} 507, 523–525. \href{http://doi.org/10.1038/nj7493-523a}{doi:10.1038/nj7493-523a} \\
Check Hayden E (2013). ``Mozilla Plan Seeks to Debug Scientific Code.'' \textbf{Nature}, 501, pp. 472-472. \href{http://doi.org/10.1038/501472a}{doi:10.1038/501472a} \\ 
Van Noorden R (2013). ``Data-Sharing: Everything on Display.'' \textbf{Nature}, 500, pp. 243-245. \href{http://doi.org/10.1038/nj7461-243a}{doi:10.1038/nj7461-243a} \\
Gewin, Virginia (2013). ``Turning Point: Carl Boettiger'' \textbf{Nature}, 493 p 711 \href{http://doi.org/10.1038/nj7434-711a}{doi:10.1038/nj7434-711a} \\
Wald, Chelsea (2010). ``Scientists Embrace Openness'' \textbf{Science}. \href{http://doi.org/10.1126/science.caredit.a1000036}{doi:10.1126/science.caredit.a1000036} 

\section{References}

Alan Hastings, Dept of Env Sci \& Policy, UC Davis \href{mailto:amhastings@ucdavis.edu}{amhastings@ucdavis.edu} \\ 
Marc Mangel, Dept of Applied Math \& Statistics, UC Santa Cruz \href{mailto:msmangel@ucsc.edu}{msmangel@ucsc.edu} \\
Matt Jones, Director of Informatics, National Center for Ecological Analysis and Synthesis \href{mailto:jones@nceas.ucsv.edu}{jones@nceas.ucsb.edu} \\

%% Simon Levin, Dept of Ecology \& Evolution, Princeton \href{mailto:slevin@princeton.edu}{slevin@princeton.edu} \\

%% Stephan Munch, Southwest Fisheries Science Center, NOAA \href{mailto:steve.munch@noaa.gov}{steve.munch@noaa.gov} \\

% Sebastian Schreiber, Dept of Evolution \& Ecology, UC Davis \href{mailto:sschreiber@ucdavis.edu}{sschreiber@ucdavis.edu} \\
%Peter Wainwright, Dept of Evolution \& Ecology, UC Davis \href{mailto:pcwainwright@ucdavis.edu}{pcwainwright@ucdavis.edu} \\
%Brian O'Meara, Dept of Ecology \& Evolution, Knoxville, TN \href{mailto:bomeara@utk.edu}{bomeara@utk.edu} \\
%Jim Sanchirico, Dept of Env Sci \& Policy, UC Davis \href{mailto:jsanchirico@ucdavis.edu}{jsanchirico@ucdavis.edu} \\
%Duncan Temple-Lang, Dept of Statistics, UC Davis \href{mailto:duncan@wald.ucdavis.edu}{duncan@wald.ucdavis.edu} \\



\end{resume}
\let\thefootnote\relax\footnote{Updated \today}
\end{document}



\section{\textnormal{Submitted}}

Samantha A. Price, Lars Schmitz, Philip S. L. Anderson, Carl Boettiger, Peter C. Wainwright. Comparing disparity between traits using the Ornstein-Uhlenbeck model: a test of functional constraint on the eyes of labrid fishes.

Carl Boettiger, Noam Ross, Alan Hastings. Early warning signals: The charted and uncharted territories.





\section{Computer \\ Languages}
R, C, OpenMP, C++, XML, JSON, \LaTeX, SWeave, bash.\\
python, html, ruby, jquery \\



\section{Coursework, Princeton \\ {\footnotesize * = Graduate course}
}

MATHEMATICS\\
Analysis in a Single Variable, Honors Linear Algebra, Analysis in Several Variables, Complex Analysis with Applications, Differential Equations, Statistics in Biology, Mathematical Modeling

BIOLOGY\\
Quant Principles in Cell Biology, Astrobiology, Advanced Lab in Molecular Biology, Honors Chemistry, Genetics, Method and Logic in Quantitative Biology*, Geomicrobiology*, Cellular and Biochemical Computation*

PHYSICS\\
Mechanics, Electromagnetism, Computational Physics Seminar,  Lagrangian Mechanics, Astronomy, Experimental Physics Seminar, Quantum Mechanics I, Quantum Mechanics II,  Thermal Physics, Advanced Physics Lab, Advanced Electromagnetism,  Biophysics* 

HUMANITIES\\
Intermediate French, Advanced French, History of Science, Cranks and Visionaries in Science, Social Revolution in Muslim World, Logic, Moral Philosophy, Shakespeare, Old English, Heroic Literature, Civilization Early Middle Ages


\section{Coursework, UC Davis}
ECOLOGY \& EVOLUTION \\
Population Biology Core Sequence, Mathematical Methods in Ecology, Theoretical Ecology, Synchrony in Ecology, Resource Economics 

COMPUTER SCIENCE \\
Algorithms, Statistical Computing, Neural Networks 

MATHEMATICS\\
Stochastic Differential Equations I \& II, Mathematical Biology 

  


